Analytic reproducibility in articles receiving open data badges at Psychological Science: An observational assessment

### 2020-07-08 manuscript/manuscript.Rmd
minor wording updates

affiliation:
  - id            : "1"
    institution   : "University of Amsterdam"
  - id            : "2"
    institution   : "Charité – Universitätsmedizin Berlin"
  - id            : "3"
    institution   : "Max Planck Institute for Evolutionary Anthropology"
  - id            : "4"
    institution   : "University of California, Los Angeles"
  - id            : "5"
    institution   : "Stanford University"
  - id            : "6"
    institution   : "Tilburg University"

@@

author_note: >
  Tom E. Hardwicke, Department of Psychology, University of Amsterdam & Meta-Research Innovation Center Berlin (METRIC-B), QUEST Center for Transforming Biomedical Research, Charité – Universitätsmedizin Berlin. Manuel Bohn, Emily Hembacher, Benjamin N. Peloquin, Benny deMayo, Bria Long, Erica J. Yoon, Michael C. Frank, Department of Psychology, Stanford University. Kyle MacDonald, Department of Communication, University of California, Los Angeles. Michèle B. Nuijten, Department of Methodology and Statistics, Tilburg School of Social and Behavioral Sciences, Tilburg University.

@@

figsintext        : yes
figurelist        : no
tablelist         : no
footnotelist      : no
lineno            : yes
mask              : no
csl               : "apa7.csl"
class             : "man"
output            : 
  papaja::apa6_pdf:
    includes:
        after_body: "supplementary_information.tex"

@@

A minimum quality standard expected of all scientific manuscripts is that any reported numerical values can be reproduced if the original analyses are repeated upon the original data [@bollen2015]. This concept is known as *analytic reproducibility* [@lebel2018; or relatedly, *computational reproducibility*[^compRepro], @stodden2018]. When a number cannot be reproduced, this minimally indicates that the process by which it was calculated has not been sufficiently documented. Non-reproducibility may also indicate that an error has occurred, either during the original calculation or subsequent reporting. Either way, the integrity of the analysis pipeline that transforms raw data into reported results cannot be guaranteed. As a result, non-reproducibility can create uncertainty about the provenance and veracity of scientific evidence, potentially undermining the credibility of any associated inferences. As a result, non-reproducibility can undermine data re-use [@hardwicke2018a], complicate replication attempts [@nuijten2018], and create uncertainty about the provenance and veracity of scientific evidence, potentially undermining the credibility of any associated inferences [@lebel2018].

@@

Difficulty establishing the analytic reproducibility of research reports has been encountered in several scientific domains, including economics, political science, behavioural ecology, and psychology [@chang2015; @eubank2016; @stodden2018; @obels2019; @hardwicke2018a; @minocher2020; but see @naudet2018]. A preliminary obstacle for many such studies is that research data are typically unavailable [@hardwicke2018; @hardwicke2020a; @wicherts2006]. Even when data can be accessed, suboptimal management and inadequate documentation can complicate data reuse [@hardwicke2018a; @kidwell2016]. These failures to adequately preserve and share earlier stages of the research pipeline can prevent downstream assessment of analytic reproducibility.

A previous study in the domain of psychology largely circumvented data availability issues by capitalizing on a mandatory open data policy introduced at the journal Cognition [@hardwicke2018a]. After assessing a sample of 35 articles with available data that had already passed initial quality checks, at least one value could not be reproduced within a 10% margin of error in 24 of the 35 (69%) articles. Reproducibility issues were resolved in 11 of the 24 articles after consultation with original authors yielded additional data or clarified analysis procedures. Ultimately, 64 of 1324 (5%) checked values could not be reproduced despite author involvement. Importantly, there were no clear indications that the reproducibility issues seriously undermined the conclusions of the original articles. Nevertheless, this study highlighted a number of quality control and research transparency issues, including suboptimal data management; unclear, incomplete, or incorrect analysis specification; and reporting errors.

@@

[^percentError]: An important caveat of this measure should be noted: large percentage differences can occur for small absolute differences when the absolute magnitude of values is small (and vice versa). Thus, when considering individual cases, quantitative measures should be evaluated in the full context of our case-by-case qualitative observations (Supplementary Information \@ref(vignettes)).

@@

Of `r data_kidwell_badge %>% nrow()` articles marked with an open data badge, Kidwell and colleagues had identified `r data_kidwell_badge_reusable %>% nrow()` with datasets that met four reusability criteria (accessible, correct, complete, and understandable). For each of these articles, one investigator (TEH) attempted to identify a coherent set of descriptive and inferential statistics (e.g., means, standard deviations, t-values, p-values; see Figure \@ref(fig:valueTypePlot)), roughly 2-3 paragraphs of text, sometimes including a table or figure, related to a ‘substantive’ finding based on ‘relatively straightforward’ analyses. We focused on substantive findings because they are the most important and straightforward analyses to ensure that our team had sufficient expertise to re-run them. In total, `r nrow(data_values)` discrete numerical values reported in `r totalArticles` articles were identified as target values. The articles were published between January 2014 and May 2015. Further information about the sample is available in Supplementary Information \@ref(sup_sample).

@@

The primary aim of the reproducibility checks was to recover the reported target values by repeating the original analysis (as described in the original articles and any additional documentation such as supplementary materials, codebook, analysis scripts) upon the available data. Attempting alternative analyses was outside the scope of the study. To minimize error and facilitate reproducibility, each reproducibility check was conducted by at least two team members who documented the reanalysis process in an R Markdown report (available at https://osf.io/hf9jy/). If articles were initially classified as not fully reproducible, we emailed the author(s) of the article and used any additional information they provided to try and resolve the issues before a final classification was determined. Additional procedural details are available in Supplementary Information \@ref(sup_design).

@@

The present study is highly comparable in goal and design to a previous study (Hardwicke et al. 2018), presenting an opportunity to synthesize their estimates of analytic reproducibility in psychology. To this end, we used random-effects models with inverse-variance weighting to meta-analyze the raw proportion estimates of article-level analytic reproducibility for the two studies, separately before and after original authors were contacted [@schwarzer2015].

@@

```{r}
# prepare information on insufficent information errors for reporting inline
insuffInfoErrors <- data_articles %>% filter(Insufficient_Information_Errors > 0) %>% nrow() # how many articles had at least 1 insufficient information error
insuffInfoErrors_percent <- insuffInfoErrors/totalArticles*100 # calculate percent
insuffInfoErrors_CIs <- propCI(insuffInfoErrors,totalArticles) # caluclate CIs
```
Prior to seeking original author involvement, all target outcomes in `r reproBefore %>% filter(reproOutcome == T) %>% pull(n)` out of the `r totalArticles` articles (`r reproBefore %>% filter(reproOutcome == T) %>% pull(percent)`) were reproducible, with the remaining `r reproBefore %>% filter(reproOutcome == F) %>% pull(n)` (`r reproBefore %>% filter(reproOutcome == F) %>% pull(percent)`) containing at least one major numerical discrepancy. After requesting input from original authors, several issues were resolved through the provision of additional information[^authorInfo] and ultimately all target outcomes in `r reproAfter %>% filter(reproOutcome == T) %>% pull(n)` (`r reproAfter %>% filter(reproOutcome == T) %>% pull(percent)`) articles were reproducible, with the remaining `r reproAfter %>% filter(reproOutcome == F) %>% pull(n)` (`r reproAfter %>% filter(reproOutcome == F) %>% pull(percent)`) articles containing at least one major numerical discrepancy. The full breakdown of reproducibility outcomes after author contact are shown in Table \@ref(tab:reproTab) and the results of a meta-analysis synthesizing the findings with those of a previous study [@hardwicke2018a] are displayed in Figure \@ref(fig:forestPlot). Aspects of `r as.english(insuffInfoErrors)` reproducibility checks could not be completed as there was insufficient information to proceed with the reanalysis. Availability of original analysis scripts appeared to provide some modest benefits in terms of reproducibility outcomes and time expenditure (see Supplementary Information \@ref(sup_results)). In no cases did the observed numerical discrepancies appear to be consequential for the conclusions stated in the original articles (see Supplementary Information \@ref(vignettes)).

@@

```{r scatterPlot, fig.cap="Scatterplot showing reanalysis p-values as a function of original p-values, classified by reproducibility outcome. Axes are on a log scale. Dashed lines represent the typical 0.05 threshold for statistical significance. For display purposes, 41 values below 0.001 are not shown. Original values reported as thresholds (e.g., p < .05) are represented by the threshold value when there was a major discrepancy and represented by the reanalysis value when there was a match.", fig.path="figs/"}
source(here('analysis','plot_reproScatter.R')) # build plot
scatterPlot # show plot
```

```{r fig.cap="Forest plot showing the proportion of articles with fully reproducible target outcomes in Hardwicke et al. (2018) and the present study before and after contacting original authors for assistance with reproducibility checks. Squares represent individual study proportions (with size proportional to meta-analytic weighting). Diamonds represent summary proportions estimated by random effects (RE) models. Error bars represent 95% confidence intervals (CIs).", fig.width=8, fig.path="figs/"}
source(here('analysis','meta_analysis.R'))
```

@@

Where possible we attempted to identify the causal locus of the reproducibility issues we encountered though this was not always possible to confirm definitively. Supplementary Figure \@ref(fig:locusPlot) shows the frequency of four types of discrete causal loci that we determined were involved in non-reproducibility and how many of these issues were resolved through author involvement. The most common issues we encountered were related to unclear, incomplete, or incorrect reporting of analytic procedures. Examples include unidentified statistical tests, unclear aggregation procedures, non-standard p-value reporting, and unreported data exclusions. Most of these issues could be resolved when original authors provided additional information. Less frequently, we encountered typographical errors and some issues related to data files, including erroneous or missing data. For many instances of non-reproducibility, the causal locus remained unidentified even after contact with original authors.

@@

timeSummary <- data_articles %>%
  mutate(activeTTC = (pilotTTC + copilotTTC)/60) %>%
  summarise(median = median(activeTTC), IQR = round(IQR(activeTTC)), min = round(min(activeTTC)), max = round(max(activeTTC)), total = round(sum(activeTTC)))
```
Team members provided concurrent estimates of their time spent on each stage of the analysis. Altogether, they estimated that they spent between `r timeSummary %>% pull(min)` and `r timeSummary %>% pull(max)` (median = `r timeSummary %>% pull(median)`, interquartile range = `r timeSummary %>% pull(IQR)`) hours actively working on each reproducibility check (Supplementary Figure \@ref(fig:timePlot); total time = `r timeSummary %>% pull(total)` hours). This estimate excludes time spent waiting on internal (within our team) and external (with original authors) communications.

@@

A reasonable expectation of any scientific manuscript is that repeating the original analyses upon the original data will yield the same quantitative outcomes [@bollen2015]. We have found that this standard of analytic reproducibility was frequently not met in a sample of Psychological Science articles receiving open data badges. Importantly, none of the reproducibility issues we encountered appeared seriously consequential for the conclusions stated in the original articles. Nevertheless, non-reproducibility highlighted fundamental quality control and documentation failures during data management, data analysis, and reporting. Furthermore, the extensive time investment required to check and establish analytic reproducibility would likely be prohibitive for many researchers interested in re-using data. The findings are consistent with a previous study which found a similar rate of non-reproducibility and identified unclear, incomplete, or incorrect analysis reporting as a primary contributing factor [@hardwicke2018a]. Although the open badges scheme introduced at Psychological Science has been associated with an increase in data availability [@kidwell2016], the current findings suggest that additional efforts may be required in order to ensure analytic reproducibility.

Some reproducibility issues were resolved through involvement of original authors, however, relying on such assistance is not ideal for several reasons: (1) it substantially increases the workload and time investment, both for researchers attempting to re-use data and for original authors; (2) important details about and materials related to the study are more likely to be forgotten or misplaced over time, reducing the ability of authors to assist [@vines2014; @minocher2020]; (3) authors may be unwilling or unable to respond, as was the case for three of the articles we examined. Author involvement highlighted that non-reproducibility was often caused by unclear, incomplete, or incorrect reporting of analytic procedures in the original papers, issues which could often be resolved through the provision of additional information or clarifications beyond what was previously reported. In other cases, authors informed us of errors in shared data files or analysis scripts, suggesting that at some stage the original data, analyses, and research report had become decoupled. In some cases, neither we nor the original authors could reproduce the target values and the causal locus of non-reproducibility remained unidentified; it was no longer possible to reconstruct the original analysis pipeline.

This study has a number of important limitations and caveats. Most pertinently, generalizing the observed reproducibility rates to other articles requires some caution as several characteristics of our sample are likely to have had a positive impact on the reproducibility rate. We specifically selected a sample of articles for which data were already available and screened against several reusability criteria [@kidwell2016]. This is relevant because most psychology articles are not accompanied by raw data or analysis scripts at all [@hardwicke2018; @hardwicke2020a; @wicherts2006], and even when data is available, suboptimal management and documentation can complicate re-use [@hardwicke2018a]. Thus, most psychology articles would likely fail a reproducibility check before reaching the stage of the analysis pipeline at which we began our assessments.

Additionally, all articles in the sample had been submitted to a leading psychology journal that had recently introduced a number of policy changes intended to improve research rigor and transparency [@eich2014]. These included the open badges scheme, removing word limits for methods and results sections, and requesting explicit disclosure of relevant methodological information like exclusions. It is likely that these new initiatives positively impacted reproducibility, either through directly encouraging adoption of reproducible research practices or attracting researchers to the journal who were already inclined to use such practices. Some evidence, for example, implies that data availability is modestly associated with a lower prevalence of statistical reporting inconsistencies [@wicherts2011].  In sum, several features of the current sample are likely to facilitate reproducibility relative to a more diverse population of psychology articles.

Whilst the current findings are concerning, non-reproducibility is fortunately a solvable problem, at least in principle. As noted above, a major barrier to analytic reproducibility is low availability of research resources like data and code [@hardwicke2020a]. Some evidence suggests that journal policies which mandate data sharing are associated with increased data availability [@hardwicke2018a; @nuijten2017], apparently more so than voluntary badge schemes [@kidwell2016]. Sharing of analysis scripts may help by providing veridical documentation of the analysis process which is not well captured in verbal prose [@hardwicke2018a]. However, as with data sharing, mere availability will not be sufficient to confer the potential benefits of analysis scripts. The utility of scripts depends on a range of factors, including clarity, structure, and documentation, as well the programming language that is used and whether it is in a proprietary format or requires special expertise to understand. In the present study, script availability appeared to offer modest benefits in terms of reproducibility outcomes and time expenditure; however, as only six articles shared scripts[^psychsci_scripts], it is difficult to draw strong conclusions about their impact from this evidence alone.

@@

Another potential target for policy intervention includes improving quality control at the journal level, potentially through independent assessment of analytic reproducibility; however, this would naturally require additional resources [for discussion see @sakaluk2014]. Some journals, such as the American Journal of Political Science, pay for a third-party institute to verify the reproducibility of all manuscripts prior to publication [@jacoby2017]. Ideally, initiatives intended to improve analytic reproducibility should undergo empirical scrutiny in order to evaluate costs and benefits and identify any policy shortfalls or unintended consequences [@hardwicke2020b].

Although journal policy is potentially helpful for incentivisation and verification, the reproducibility of a scientific manuscript is fundamentally within the control of its authors. Fortunately, a variety of tools are now available that allow for the writing of entirely reproducible research reports in which data, analysis code, and research reports are intrinsically linked [e.g., @vuorre2020]. It should be noted that ensuring the reproducibility of a scientific manuscript requires a non-trivial time investment and presently, there is room for improvement in the data management and analysis practices adopted by psychological researchers [e.g., @borghi2020]. Continued development of user-friendly tools that facilitate reproducibility and dedicated training may help to reduce this burden. Additionally, the costs of ensuring reproducibility could be offset by the benefits of improved workflow efficiency, error detection and mitigation, and potential for data re-use. Detailed guidance on data sharing, data management, and analytic reproducibility is available to support psychological scientists seeking to improve these practices in their own research [@klein2018]. The present manuscript is an illustration of these practices in action (https://doi.org/10.24433/CO.6557927.v1).

@@

TEH and MCF designed the study. TEH, MB, KM, EH, MBN, BNP, BdM, BL, EJY, and MCF conducted reproducibility checks. TEH performed the data analysis. TEH and MCF wrote the manuscript. MB & MBN provided feedback on the manuscript. All authors gave final approval for publication.

@@

```{r render_appendix, include=FALSE}
render_appendix("supplementary_information.Rmd")
```

>>>>

affiliation:
  - id            : "1"
    institution   : "Department of Psychology, University of Amsterdam"
  - id            : "2"
    institution   : "Meta-Research Innovation Center Berlin (METRIC-B), QUEST Center for Transforming Biomedical Research, Charité – Universitätsmedizin Berlin"
  - id            : "3"
    institution   : "Department of Comparative Cultural Psychology, Max Planck Institute for Evolutionary Anthropology"
  - id            : "4"
    institution   : "Department of Communication, University of California, Los Angeles"
  - id            : "5"
    institution   : "Department of Psychology, Stanford University"
  - id            : "6"
    institution   : "Department of Methodology and Statistics, Tilburg School of Social and Behavioral Sciences, Tilburg University"

@@

author_note: >

@@

figsintext        : yes
figurelist        : no
tablelist         : no
footnotelist      : no
lineno            : yes
mask              : no
csl               : "apa7.csl"
class             : "man"
output            : 
  papaja::apa6_word

@@

A minimum quality standard expected of all scientific manuscripts is that any reported numerical values can be reproduced if the original analyses are repeated upon the original data [@bollen2015]. This concept is known as *analytic reproducibility* [@lebel2018; or relatedly, *computational reproducibility*[^compRepro], @stodden2018]. When a number cannot be reproduced, this minimally indicates that the process by which it was calculated has not been sufficiently documented. Non-reproducibility may also indicate that an error has occurred, either during the original calculation or subsequent reporting. Either way, the integrity of the analysis pipeline that transforms raw data into reported results cannot be guaranteed. As a result, non-reproducibility can undermine data re-use [@hardwicke2018a], complicate replication attempts [@nuijten2018], and create uncertainty about the provenance and veracity of scientific evidence, potentially undermining the credibility of any associated inferences [@lebel2018].

@@

Difficulty establishing the analytic reproducibility of research reports has been encountered in several scientific domains, including economics, political science, behavioural ecology, and psychology [@chang2015; @eubank2016; @stodden2018; @obels2019; @hardwicke2018a; @minocher2020; but see @naudet2018]. A preliminary obstacle for many such studies is that research data are typically unavailable [@hardwicke2018; @hardwicke2020a; @wicherts2006]. Even when data can be accessed, suboptimal management and inadequate documentation can complicate data reuse [@hardwicke2018a; @kidwell2016]. These failures to adequately preserve and share earlier stages of the research pipeline typically prevent downstream assessment of analytic reproducibility.

A previous study in the domain of psychology largely circumvented data availability issues by capitalizing on a mandatory data sharing policy introduced at the journal Cognition [@hardwicke2018a]. In a sample of 35 articles with available data that had already passed initial quality checks, 24 (69%) articles contained at least one value that could not be reproduced within a 10% margin of error. Reproducibility issues were resolved in 11 of the 24 articles after consultation with original authors yielded additional data or clarified analytic procedures. Ultimately, 64 of 1324 (5%) checked values could not be reproduced despite author involvement. Importantly, there were no clear indications that the reproducibility issues seriously undermined the conclusions of the original articles. Nevertheless, this study highlighted a number of quality control and research transparency issues, including suboptimal data management; unclear, incomplete, or incorrect analysis specification; and reporting errors.

@@

[^percentError]: An important caveat of this measure should be noted: large percentage differences can occur when the absolute magnitude of values is small (and vice versa). Thus, when considering the consequences of non-reproducibility for individual cases, quantitative measures should be evaluated in the full context of our qualitative observations (Supplementary Information \@ref(vignettes)).

@@

Of `r data_kidwell_badge %>% nrow()` articles marked with an open data badge, Kidwell and colleagues had identified `r data_kidwell_badge_reusable %>% nrow()` with datasets that met four reusability criteria (accessible, correct, complete, and understandable). For each of these articles, one investigator (TEH) attempted to identify a coherent set of descriptive and inferential statistics (e.g., means, standard deviations, t-values, p-values; see Figure \@ref(fig:valueTypePlot)), roughly 2-3 paragraphs of text, sometimes including a table or figure, related to a ‘substantive’ finding based on ‘relatively straightforward’ analyses. We focused on substantive findings because they are the most important and straightforward analyses to ensure that our team had sufficient expertise to re-run them. In total, `r nrow(data_values)` discrete numerical values reported in `r totalArticles` articles published between January 2014 and May 2015 were designated as target values. Further information about the sample is available in Supplementary Information \@ref(sup_sample).

@@

The aim of the reproducibility checks was to recover the target original values by repeating the original analysis (as described in the original articles and any additional documentation such as supplementary materials, codebook, analysis scripts) upon the original data. Attempting alternative analyses was outside the scope of the study, even if the original analysis seemed sub-optimal or erroneous.

To minimize error and facilitate reproducibility, each reproducibility check was conducted by at least two team members who documented the reanalysis process in an R Markdown report (available at https://osf.io/hf9jy/). If articles were initially classified as not fully reproducible, we emailed the author(s) of the article and used any additional information they provided to try and resolve the issues before a final classification was determined. Additional procedural details are available in Supplementary Information \@ref(sup_design).

@@

The present study is highly comparable in goal and design to a previous study (Hardwicke et al. 2018), creating an opportunity to synthesize their estimates of analytic reproducibility. To this end, we used random-effects models with inverse-variance weighting to meta-analyze the raw proportion estimates of article-level analytic reproducibility for the two studies, separately before and after original authors were contacted [@schwarzer2015].

@@

```{r}
# prepare information on insufficent information errors for reporting inline
insuffInfoErrors <- data_articles %>% filter(Insufficient_Information_Errors > 0) %>% nrow() # how many articles had at least 1 insufficient information error
insuffInfoErrors_percent <- insuffInfoErrors/totalArticles*100 # calculate percent
insuffInfoErrors_CIs <- propCI(insuffInfoErrors,totalArticles) # caluclate CIs

# prepare information on no author response
noResponse <- data_articles %>% filter(finalOutcome == 'Not reproducible\nwithout author\ninvolvement') %>% nrow()
```
Prior to seeking original author involvement, all target values in `r reproBefore %>% filter(reproOutcome == T) %>% pull(n)` out of the `r totalArticles` articles (`r reproBefore %>% filter(reproOutcome == T) %>% pull(percent)`) were reproducible, with the remaining `r reproBefore %>% filter(reproOutcome == F) %>% pull(n)` articles (`r reproBefore %>% filter(reproOutcome == F) %>% pull(percent)`) containing at least one major numerical discrepancy. After requesting input from original authors, several issues were resolved through the provision of additional information[^authorInfo] and ultimately all target values in `r reproAfter %>% filter(reproOutcome == T) %>% pull(n)` (`r reproAfter %>% filter(reproOutcome == T) %>% pull(percent)`) articles were reproducible, with the remaining `r reproAfter %>% filter(reproOutcome == F) %>% pull(n)` (`r reproAfter %>% filter(reproOutcome == F) %>% pull(percent)`) articles containing at least one major numerical discrepancy. In `r as.english(noResponse)` cases authors did not respond and in `r as.english(insuffInfoErrors)` cases there was insufficient information to proceed with the reanalysis. The full breakdown of reproducibility outcomes after author contact are shown in Table \@ref(tab:reproTab) and the results of a meta-analysis synthesizing the findings with those of a previous study [@hardwicke2018a] are displayed in Figure \@ref(fig:forestPlot). In no cases did the observed numerical discrepancies appear to be consequential for the conclusions stated in the original articles (see Supplementary Information \@ref(vignettes)).

@@

```{r scatterPlot, fig.cap="Scatterplot showing reanalysis p-values as a function of original p-values, classified by reproducibility outcome. Axes are on a log scale. The diagonal line represents perfect consistency between reanalysis and original values. Dashed lines represent the typical alpha threshold (0.05) for statistical significance. Original values reported relative to thresholds (e.g., p < .05) are represented by the threshold value when there was a major discrepancy and represented by the reanalysis value when there was a match. For display purposes, 41 values below 0.001 are not shown.", fig.path="figs/"}
source(here('analysis','plot_reproScatter.R')) # build plot
scatterPlot # show plot
```

```{r fig.cap="Forest plot showing the proportion of articles with fully reproducible target values in Hardwicke et al. (2018) and the present study before and after contacting original authors for assistance with reproducibility checks. Squares represent individual study proportions (with size proportional to meta-analytic weighting). Diamonds represent summary proportions estimated by random effects (RE) models. Error bars represent 95% confidence intervals (CIs).", fig.width=8, fig.path="figs/"}
source(here('analysis','meta_analysis.R'))
```

@@

Where possible we attempted to identify the causal locus of the reproducibility issues we encountered though this was not always possible to confirm definitively. Supplementary Figure \@ref(fig:locusPlot) shows the frequency of four types of discrete causal loci that we determined were involved in non-reproducibility and how many of these issues were resolved through original author input. The most common issues we encountered were related to unclear, incomplete, or incorrect reporting of analytic procedures. Examples include unidentified statistical tests, unclear aggregation procedures, non-standard p-value reporting, and unreported data exclusions. Most of these issues could be resolved when original authors provided additional information. Less frequently, we encountered typographical errors and some issues related to data files, including erroneous or missing data. For many instances of non-reproducibility, the causal locus remained unidentified even after contact with original authors.

@@

timeSummary <- data_articles %>%
  mutate(activeTTC = (pilotTTC + copilotTTC)/60) %>%
  summarise(median = median(activeTTC), IQR = round(IQR(activeTTC)), min = round(min(activeTTC)), max = round(max(activeTTC)), total = round(sum(activeTTC)))
```
Team members provided concurrent estimates of their time spent on each stage of the analysis. Altogether, they estimated that they spent between `r timeSummary %>% pull(min)` and `r timeSummary %>% pull(max)` (median = `r timeSummary %>% pull(median)`, interquartile range = `r timeSummary %>% pull(IQR)`) hours actively working on each reproducibility check (Supplementary Figure \@ref(fig:timePlot); total time = `r timeSummary %>% pull(total)` hours). This estimate excludes time spent waiting on internal (within our team) and external (with original authors) communications. Availability of original analysis scripts appeared to provide some modest benefits in terms of reproducibility outcomes and time expenditure (see Supplementary Information \@ref(sup_results)).

@@

A reasonable expectation of any scientific manuscript is that repeating the original analyses upon the original data will yield the same quantitative outcomes [@bollen2015]. We have found that this standard of analytic reproducibility was frequently not met in a sample of Psychological Science articles receiving open data badges. Importantly, none of the reproducibility issues we encountered appeared seriously consequential for the conclusions stated in the original articles (though in three cases insufficient information about original analytic procedures prevented us completing our reproducibility checks). Nevertheless, non-reproducibility highlighted fundamental quality control and documentation failures during data management, data analysis, and reporting. Furthermore, the extensive time investment required to check and establish analytic reproducibility would likely be prohibitive for many researchers interested in building upon and re-using data, for example to conduct robustness checks, novel analyses, or meta-analyses. The findings are consistent with a previous study which found a similar rate of non-reproducibility and identified unclear, incomplete, or incorrect analysis reporting as a primary contributing factor [@hardwicke2018a]. Although the open badges scheme introduced at Psychological Science has been associated with an increase in data availability [@kidwell2016], the current findings suggest that additional efforts may be required in order to ensure analytic reproducibility.

Some reproducibility issues were resolved after input from original authors, however, relying on such assistance is not ideal for several reasons: (1) it substantially increases the workload and time investment, both for researchers attempting to re-use data and for original authors; (2) information related to the study is more likely to be forgotten or misplaced over time, reducing the ability of authors to assist [@vines2014; @minocher2020]; (3) authors may be unwilling or unable to respond, as was the case for three of the articles we examined. Author provision of additional information or clarifications beyond what was previously reported highlighted that non-reproducibility was often caused by unclear, incomplete, or incorrect reporting of analytic procedures in published papers. In some cases, authors informed us of errors in shared data files or analysis scripts, suggesting that at some stage the original data, analyses, and research report had become decoupled. In some cases, neither we nor the original authors could reproduce the target values and the causal locus of non-reproducibility remained unidentified; it was no longer possible to reconstruct the original analysis pipeline.

This study has a number of important limitations and caveats. Most pertinently, generalizing the observed reproducibility rates to other articles requires some caution as several characteristics of our sample are likely to have had a positive impact on the reproducibility rate. We specifically selected a sample of articles for which data were already available and screened against several reusability criteria [@kidwell2016]. By contrast, most psychology articles are unlikely to be accompanied by raw data or analysis scripts [@hardwicke2018; @hardwicke2020a; @wicherts2006], and even when data is available, suboptimal management and documentation can complicate re-use [@hardwicke2018a]. Consequently, most psychology articles would likely fail a reproducibility check before reaching the stage of the analysis pipeline at which we began our assessments.

Additionally, all articles in the sample had been submitted to a leading psychology journal that had recently introduced a number of policy changes intended to improve research rigor and transparency [@eich2014]. These included the open badges scheme, removing word limits for methods and results sections, and requesting explicit disclosure of relevant methodological information like exclusions. It is likely that these new initiatives positively impacted reproducibility, either through directly encouraging adoption of more rigorous research practices or attracting researchers to the journal who were already inclined to use such practices [@bastian2017]. Some evidence, for example, implies that data availability is modestly associated with a lower prevalence of statistical reporting inconsistencies [@wicherts2011].  In sum, several features of the current sample are likely to facilitate reproducibility relative to a more representative population of psychology articles.

Whilst the current findings are concerning, non-reproducibility is fortunately a solvable problem, at least in principle. Journals are well-situated to influence practices related to research transparency; for example, journal data sharing mandates have been associated with marked increases in data availability [@hardwicke2018a; @nuijten2017]. Further requirements to share analysis scripts may also enhance reproducibility as veridical documentation of the analysis process is often poorly captured in verbal prose [@hardwicke2018a]. However, as with data sharing, mere availability may not be sufficient to confer the potential benefits of analysis scripts. The utility of scripts will likely depend on a range of factors, including clarity, structure, and documentation, as well the programming language that is used and whether it is stored in a proprietary format or requires special expertise to understand. In the present study, script availability appeared to offer modest benefits in terms of reproducibility outcomes and time expenditure; however, as only six articles shared scripts[^psychsci_scripts], it is difficult to draw strong conclusions about their impact from this evidence alone. Journals could also conduct independent assessment of analytic reproducibility prior to publication, as has been adopted by the American Journal of Political Science [@jacoby2017]; however, this would naturally require additional resources [for discussion see @sakaluk2014]. Ideally, initiatives intended to improve analytic reproducibility should undergo empirical scrutiny in order to evaluate costs and benefits and identify any policy shortfalls or unintended consequences [@hardwicke2020b].

@@

Although journal policy is potentially helpful for incentivisation and verification, the reproducibility of a scientific manuscript is fundamentally under the control of its authors. Fortunately, a variety of tools are now available that allow for the writing of entirely reproducible research reports in which data, analysis code, and prose are intrinsically linked [e.g., @vuorre2020]. It should be noted that ensuring the reproducibility of a scientific manuscript requires a non-trivial time investment and presently, there is room for improvement in the data management and analysis practices adopted by psychology researchers [e.g., @borghi2020]. Continued development of user-friendly tools that facilitate reproducibility and dedicated reproducibility training may help to reduce this burden. Additionally, the costs of ensuring reproducibility could be offset by the benefits of improved workflow efficiency, error detection and mitigation, and opportunities for data re-use. Detailed guidance on data sharing, data management, and analytic reproducibility is available to support psychological scientists seeking to improve these practices in their own research [@klein2018]. The present manuscript is an illustration of these practices in action (https://doi.org/10.24433/CO.6557927.v1).

@@

TEH and MCF designed the study. TEH, MB, KM, EH, MBN, BNP, BdM, BL, EJY, and MCF conducted the reproducibility checks. TEH performed the data analysis. TEH and MCF wrote the manuscript. MB and MBN provided feedback on the manuscript. All authors gave final approval for publication.

@@

<div id = "refs"></div>

```{r child = "supplementary_information.Rmd"}
```
